### 2014-10-22 paper/include/raidr.tex
durr. hata bäsk....
derr

The implementation is realized by modifying the MC. To minimize the storage needed for keeping track of bin members, Bloom filters are used. Thanks to this, only \textit{1.25 KB} storage is needed for a \textit{32 GB} DRAM with the default configuration, which becomes 0.037 ppm. The storage requirement increases together with the number of bins used, while the granularity, thereby the decrease in refresh operations, of the technique becomes higher with more bins. Similarly to the number of bins, the size chosen for the Bloom filters also affects the storage overhead.

Liu et al. evaluates twelve different configurations ranging from one bin with small Bloom filters to three bins with large Bloom filters. The latter gives the highest decrease in refresh operations but needs \textit{65.25 KB} of memory, while the first only needs \textit{64 B} but have much smaller impact on the number of refreshes performed. The default configuration is a trade of between these two extremes.

>>>>

The technique is realized by modifying the MC. To minimize the storage needed for keeping track of bin members, Bloom filters are used. Thanks to this, only \textit{1.25 KB} storage is needed for a \textit{32 GB} DRAM with the default configuration, which becomes 0.037 ppm. The storage requirement increases together with the number of bins used, while the granularity, thereby the decrease in refresh operations, of the technique becomes higher with more bins. Similarly to the number of bins, the size chosen for the Bloom filters also affects the storage overhead.

Liu et al. evaluates twelve different configurations ranging from one bin with small Bloom filters to three bins with large Bloom filters. The latter gives the highest decrease in refresh operations but needs \textit{65.25 KB} of memory, while the first only needs \textit{64 B} but have much smaller impact on the number of refreshes performed. The default configuration is a trade of between these two extremes, and with it, a performance improvement of 4.1\% and a decrease in power consumption by 8.3\% is achieved in a \textit{32 GB} system compared to CBR.
